On exponential sums arising from the classical doubling method

### 2025-03-20 paper.tex
Adding the 1+ case

@@

To summarize, we have
$$\sum_{\substack{x \in \NormOneGroup{2m}\\
		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
$$\sum_{\substack{x \in \NormOneGroup{2m}\\
		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$

>>>>

\begin{remark}
	Changing variables $x \mapsto \to x$, we have that \begin{align*}
		& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
				x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
			=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
	\end{align*}
\end{remark}

@@

To summarize, we have
\begin{align*}
	& \sum_{\substack{x \in \NormOneGroup{2m}\\
			x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) \\
		=& q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),
\end{align*}
where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
$$\sum_{\substack{x \in \NormOneGroup{2m}\\
		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
\begin{remark}
	Changing variables $x \mapsto -x$, we have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
			x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
\end{remark}
